% To update resume.pdf, run the following command in PowerShell from your project root:
% & "C:\Users\reed_\AppData\Local\Programs\MiKTeX\miktex\bin\x64\pdflatex.exe" -output-directory="assets/pdfs" "_latex/resume.tex"
% This will compile resume.tex and place resume.pdf in assets/pdfs/resume.pdf.
% Then commit and push the updated PDF to GitHub.
%-------------------------
% Resume in Latex
% Author : Nicolas Reed (adapted from Jake Gutierrez template)
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames]{xcolor} % gives access to RoyalBlue
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Uncomment to change the font
% \usepackage[sfdefault]{FiraSans}
% \usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable / ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Nicolas Reed} \\ \vspace{1pt}
    \small (669)~242{-}9012 $\vert$ 
    \href{mailto:reednicolas@berkeley.edu}{\underline{reednicolas@berkeley.edu}} $\vert$ 
    \href{https://linkedin.com/in/reednicolas}{\underline{linkedin.com/in/reednicolas}}
    $\vert$ 
    \href{https://reed-nicolas.github.io/}{\underline{reed-nicolas.github.io}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Berkeley}{GPA: 3.66/4.00}
      {B.S.\ Electrical Engineering \& Computer Sciences (EECS)}{Expected May 2027}

      %–– small vertical gap ––
      \vspace{5pt} % adjust to taste (1–2 pt works well)

      {\small\textbf{Relevant coursework:} Digital Design and Integrated Circuits with FPGA Lab (in progress), Computer Architecture and Machine Structures, Operating Systems (in progress), Signals and Circuits~I~\&~II, Data Structures, Structure and Interpretation of Computer Programs, Foundations of Data Science}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sandisk}{Milpitas, CA}
      {Software Development Intern}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Analyzed and reconciled CMDB and inventory data for 40,000+ virtual machines using Pandas, enabling automated cleansing and transformation workflows that identified gaps, standardized records, and generated actionable migration plans for a cloud provider transition.}
        \resumeItem{Streamlined license management and contract summarization for 10,000 enterprise applications by developing an AI assistant using LlamaIndex and NLP, delivering actionable insights that improved compliance and reduced spend.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://slice.eecs.berkeley.edu/}{\underline{UC Berkeley SLICE Lab}}}{Berkeley, CA}
      {Undergraduate Research Assistant - advised by \href{https://sagark.org/}{\underline{Professor Sagar Karandikar}}}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Integrate AI tooling to improve usability of Chipyard and FireSim frameworks for RISC‑V hardware development.}
        \resumeItem{Extend RISC-V hardware components for architectural research by analyzing and simulating designs using Verilog and Chisel within the Chipyard toolchain.}
      \resumeItemListEnd

    \resumeSubheading
      {UC Berkeley Electrical Engineering \& Computer Sciences (EECS)}{Berkeley, CA}
      {Head Teaching Assistant}{June 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Support 1,200+ students with C, RISC-V, Python, and Logisim through office hours and an online forum.}
        \resumeItem{Host weekly lab sections for 50+ students, guiding programming exercises and problem-solving practice.}
        \resumeItem{Develop weekly homework and lab assignments, and maintain course infrastructure using GitHub and Docker.}
        \resumeItem{Earned a 4.67/5.00 average teaching rating and ranked third in student acknowledgements on course feedback.}
        \resumeItem{Answer 1{,}500+ student questions per semester to lead online forum engagement.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.micross.com/home/global/north-america/silicon-turnkey-solutions-milpitas-ca}{\underline{Micross Components - Silicon Turnkey Solutions}}}{Milpitas, CA}
      {Engineering Intern}{July 2023 -- Aug. 2023}
      \resumeItemListStart
        \resumeItem{Conducted mechanical and PCB testing on 1,000+ devices, translating results into actionable insights via Excel.}
        \resumeItem{Organized 500+ items and launched a project to boost Cleanroom productivity via preventative maintenance.}
        \resumeItem{Resolved a test issue by documenting compromised semiconductors and identifying the damage stage.}
        \resumeItem{Improved operational efficiency by creating setup sheets and updating data packages to ensure accuracy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Multistage Pipelined RISC{-}V CPU}}{2025}
      \resumeItemListStart
        \resumeItem{Designed a three-stage pipelined RISC-V CPU supporting 40+ I/R/B/S/J-type instructions for arithmetic, logic, memory, and control flow operations.}
        \resumeItem{Built the ALU, register file, and immediate generator to enable modular instruction execution.}
        \resumeItem{Implemented hazard detection and control logic to resolve data and control hazards and minimize stalls.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Linguistic Data Analysis and Visualization Tools}}{2024}
      \resumeItemListStart
        \resumeItem{Developed a browser-based tool that visualizes word usage over time by processing large CSV datasets.}
        \resumeItem{Created a semantic network modeling word relationships using graph traversal for efficient lookup and analysis.}
        \resumeItem{Practiced test driven development to ensure correctness and performance across modular Java packages.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Scheme Interpreter}}{2024}
      \resumeItemListStart
        \resumeItem{Implemented an interpreter for a subset of Lisp (Scheme) in Python, supporting core expressions and syntax.}
        \resumeItem{Applied semantic and lexical analysis techniques that machines use to evaluate and execute code.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{\textbf{Languages}: C, Python, Verilog, RISC{-}V, Chisel, SQL, MATLAB, Lisp (Scheme) \\
          \textbf{Tools \& Frameworks}: Git, GDB, Valgrind, Pandas, NumPy, Logisim, Digilent WaveForms, LTSpice, Matplotlib}} 
\end{itemize}

\end{document}